---
title: "Rsample and time series"
output: html_notebook
---

I don't remember whence is this coming from. 

```{r, comment = ""}
knitr::opts_chunk$set(comment = "", echo = T)

library(tidyverse)
library(tsibble)
library(rsample)

data(co2)
``` 

`co2` data is the monthly times series of CO$_2$ from Jan 1956 to Dec 1994. As a standard class `r class(co2)` object, it is notoriously hard to work around with. So the best thing is to convert it to a more practical format, such as a _tsibble_: 

```{r}
co2 <- as_tsibble(co2) %>% 
  rename(time = index) %>% 
  mutate(time = as.Date(time))

co2 

```

So much better. Even if the printout on rmarkdown is not pretty (we could use `knitr::kable` or work it a bit with the `formattable` package), it is actually easier to extract info from it. 

For example, we can get the first and the last dates quite easily: 

```{r}
min(co2$time) 
max(co2$time)
```

Ok, continuing. `rsample::rolling_origin` can do a resampling of the original time series taking into account the time nature of the series: instead of randomly selecting points from the series (as you would with non-timed data) to produce _n_ samples, it produces samples whose data points are consecutive. 

The help file is not particularly... well, helful. In particular, the parameters `initial`, `assess` and `cumulative` are confusing. 

* initial means ... TBC
* assess means ... TBC
* cumulative means ... TBC


```{r}
(roll_co2 <- rolling_origin(
  co2, 
  initial = 12*30, 
  assess = 12,
  cumulative = F
))

```

Let's have a look at it:

```{r}
roll_co2 %>% pluck("splits") %>% pluck(1) %>% str
```

It's actually a pretty complicated structure: We have the `data` with `time`, `value`, and a bunch of attributes such as indices, names and intervals. In addition to the `data` we have an _internal_ index (1, 2, 3...) `in_id` and an external one (matching the original time series, I presume) `out_id`. Finally, an `id` for the slice is provided. 

```{r}
get_date <- function(x) {
  min(assessment(x)$time)
}

start_date <- map(roll_co2$splits, get_date)
roll_co2$start_date <- do.call("c", start_date)

roll_co2

library(forecast)

fit_model <- function(x, ...){
  x %>% 
    analysis() %>% 
    tk_ts(start = .$time[[1]] %>% as.yearmon(), 
          frequency = 12, 
          silent = T) %>% 
    auto.arima(...)
}

library(purrr)

roll_co2$arima <- map(roll_co2$splits, fit_model)

roll_co2$arima[[1]]
```

